When Subgraph Isomorphism is Really Hard, and Why This Matters for Graph Databases

### 2017-11-10 paper/paper.tex
Typso
Better word

The Glasgow and LAD solvers are constraint programming inspired algorithms (although they use
dedicated data structures, and do not use a constraint programming toolkit). Constraint programming
is a field concerned with solving \emph{constraint satisfaction} problems. In such a problem, we
have a set of \emph{variables}, each of which has a \emph{domain} of \emph{values}. We also have a
set of \emph{constraints}. The objective is to assign each variable a value from its domain, whilst
respecting every constraint. This is done using a combination of \emph{inference}, which eliminates
infeasible values from domains, and backtracking search. This search is driven by
\emph{variable-ordering} heuristics, which select which unassigned variable to branch on, and
\emph{value-ordering} heuristics, which select which value to try giving that variable. If at any
point during search a \emph{domain wipeout} occurs (that is, if every value is removed from any
domain), the algorithms will backtrack immediately.

@@

\subsection{A Phase Transitions when Varying Pattern Edge Density}

>>>>

The Glasgow and LAD solvers are constraint programming inspired algorithms (although they use
dedicated data structures, and do not use a constraint programming toolkit). Constraint programming
is a field concerned with solving \emph{constraint satisfaction} problems. In such a problem, we
have a set of \emph{variables}, each of which has a \emph{domain} of \emph{values}. We also have a
set of \emph{constraints}. The objective is to assign each variable a value from its domain, whilst
respecting every constraint. This is done using a combination of \emph{inference}, which eliminates
infeasible values from domains, and backtracking search. This search is driven by
\emph{variable-ordering} heuristics, which select which unassigned variable to branch on, and
\emph{value-ordering} heuristics, which select which value to try giving that variable. If at any
point during search a \emph{domain wipeout} occurs (that is, if every value is removed from any
domain), the search will backtrack immediately.

@@

\subsection{A Phase Transition when Varying Pattern Edge Density}
